A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-29 UAM2014/Article/article.tex
la2pdf commit - 2014:04:29	11:10:06	(Tue29.Apr)

@@

>>>>

% To obtain optimal classification performance using template matching techniques a large set of templates must be availab

We have developed a simulator for synthetic aperture sonar (SAS) that creates object templates very quickly with the aid of the massive computing power in graphics processing units (GPUs). It uses OpenGL to render a optical 2D image and depth map from the 3D model and seafloor representation, and OpenCL compute a sonar template based on this.

By coincidence this implementation is not so different from the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC). They both take advantage of graphics processing to render a 2D image from 3D models, are designed for side-looking sonar, and assume a Lambertian scattering model. However, SIGMAS+ is not designed for creating object templates, and adds e.g. noise to the images for them to more closely

@@

OpenGL is a popular, well-matured, multi-platform application programming interface (API) for rendering 2D and 3D vector graphics.
